---
title: "Dep_results"
author: "OT"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(kableExtra)
library(formattable)
library(here)
library(dplyr)

load(here("work.RData"))

```

```{r result_overall, echo=FALSE}

options(kableExtra.html.bsTable = TRUE)

var_labels <- c("Year", "Simple Mean", "Population weighted mean")

val  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN import dependency ratio for GS countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_P  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN import dependency ratio for Periphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_SP  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN import dependency ratio for SemiPeriphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")
```


```{r result_sector, echo=FALSE}

options(kableExtra.html.bsTable = TRUE)

var_labels <- c("Year", "Simple Mean", "Population weighted mean")

val_energy  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN energy production import dependency ratio for GS countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_energy_P  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN energy production import dependency ratio for Periphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_energy_SP  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN energy production import dependency ratio for SemiPeriphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_food  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN Food production import dependency ratio for GS countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_food_P  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN Food production import dependency ratio for Periphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")

val_food_SP  %>%
  kbl(digits = 2, col.names = var_labels, caption = "GN Food production import dependency ratio for SemiPeriphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px")  %>%
  footnote(general = "Values are proportion of total imports")


```

## Country listing

The countries are somewhat arbitrarily bucketed into P and SemiP, wo we have to discuss that because there hasn't been a comprehensive division done by anyone that I could find of all countries into P and SP
Gs and GN division is clearer but that might require looking into as well because there can be a couple of different methods (i.e. IMF designation by income or something else?)

```{r country_lists, echo=FALSE}

options(kableExtra.html.bsTable = TRUE)

ctrys %>%
  kbl(caption = "List of countries in analysis") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px") %>%
  footnote(general = "GS countries as listed in JH's TiVa paper, need to update ref
           Periphery & SemiP as defined in Wallerstein's work but custom updates so need to confirm")

ctrys  %>%
  filter(GS_GN == "GS") %>%
  kbl(caption = "List of GS countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px") %>%
  footnote(general = "GS countries as listed in JH's TiVa paper, need to update ref")

ctrys  %>%
  filter(C_P_SP == "SP") %>%
  kbl(caption = "List of SemiPeriphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px") %>%
  footnote(general = "SemiPeriphery as defined in Wallerstein's work but custom updates so need to confirm")

ctrys  %>%
  filter(C_P_SP == "P") %>%
  kbl(caption = "List of Periphery countries") %>%
  kable_styling(bootstrap_options = c("striped","hover", "condensed") , full_width = F ) %>%
  scroll_box(height = "300px") %>%
  footnote(general = "Periphery as defined in Wallerstein's work but custom updates so need to confirm")

```


